---
title: "My answers"
author: "My name"
date: "2022-11-14"
output: html_document
---




# 1. Simple linear model

> In order to tryout linear models in _R_ we are going to use the `blood_fat` dataset which contains the *age* (in years), *weight* (in kg) and  measured *fat concentrations* (units were not mentioned) in blood samples of different subjects.

## Relation of blood fat content and age

We would like to determine whether the blood concentration in fat is related to the age of the subjects.

(@) load the data (`csv`) available [here](data/blood_fat.csv) in R

```{r}
# Write your answer here
```



### Visualization

(@) If the goal would be to guess the fat concentration knowing someones age, find out which are the **response** and **predictor** variables and draw the according scatter plot.
(@) Add a regression line (without the confidence interval ribbon).
```{r}
# Write your answer here
```


(@) Add a new column to the `blood_fat` data frame containing the expected fat levels from the linear model.
    - For each subject in the data frame, add these predicted values as **red points** on your previous plot.
    - Using `geom_segment()`, connect the expected values to the measured values as **dotted lines**.

```{block, opts.label = "tip"}
Remember to use the appropriate `broom` function after the linear model, to fetch all those information in one tibble
```


```{r}
# Write your answer here
```


(@) Calculate the **slope** and **intercept** of the regression line

```{r}
# Write your answer here
```


(@) Draw a **dashed lightblue** line using **explicitly** the values you calculated in the previous question

```{r}
# Write your answer here
```



### Calculate $R^2$

You learned that $R^2$ can be calculated as follows:

  $$R^2 = 1- \frac{\sum(y_i - \hat{y_i})^2}{\sum(y_i - \bar{y})^2} = 1- \frac{RSS}{TSS}$$

(@) The length of the dotted lines you just represented are related to a term of this equation. Which one?
(@) Using `mutate()`, add the length of each dotted line to the `blood_fat` data frame.

```{r}
# Write your answer here
```


(@) What do these length represent? Which functions in _R_ generates these values?

```{r}
# Write your answer here
```


(@) Calculate $RSS$, $TSS$ and $R^2$

```{r}
# Write your answer here
```


```{r}
# Write your answer here
```


(@) Is there really a relationship between blood fat content and age? What does the value of $R^2$ tell you?

```{r}
# Write your answer here
```

### Checking the residuals of the model

(@) Residuals's mean
    + What is the expectation for the residuals's mean?
    + Compute the residuals's mean for the fat explained by age model.
```{r}
# Write your answer here
```


(@) Can the measures appropriately be modelled in this way? Draw two diagnosis plots using `ggplot2`
    + In the first draw the residuals on the _y_ axis and the estimated values on the _x_ axis
    + Your second one should be a quantile-quantile plot.


```{block, opts.label = "tip"}
The package `ggfortify` and the function `autoplot(fit)` can produce the classic 4 diagnostic plots with no efforts
```

```{r}
# Write your answer here
```


### Relation of blood fat content and weight

(@) Change predictor and use `weight` instead of `age` to predict the fat concentration

```{r}
# Write your answer here
```


(@) Check the summary and diagnostic plots for this regression

```{r}
# Write your answer here
```


```{r}
# Write your answer here
```


(@) Can the blood content in fat be explained by the weight of the subject?

```{r}
# Write your answer here
```



